Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2022-11-30 docs/manuscript/manuscript.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}

@@

\subsection*{Assessing the Reproducibility of Geographic Research}
Reproducibility has only recently moved forward on Geography's disciplinary research agenda.

Direct and indirect assessments of research reproducibility

Geographic researchers are beginning to address these questions by conducting direct and indirect assessments of the reproducibility of geographic research. 
However, only a small number of such studies currently exist resulting in a similarly limited set of evidence about reprodubibility within the discipline.

There is reason to believe that each of these factors is present in geography, but limited evidence because published reproductions have not yet become common in geography. 
The small number of studies that have attempted to assess the reproducibility of geographic research by recreating existing work suggest that many studies cannot be fully reproduced \citep{Kedron2021ssrn, nust2018, ostermann2021}, or are simply missing components needed to attempt a reproduction \citep{Kedron_VijayanRP, konkol2019, ostermann2021}.
For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be reproduced, or could only be reproduced with significant effort. 
A related effort to reproduce 31 papers published in the conference series of the Association of Geographic Information Laboratories in Europe \citep{Nust_AGILE_2020, Nust2021AGILE, Nust_AGILE_2022} similarly identified the inaccessibility of data, code, and information about the computational environment as key barriers to recreating results. 
\citet{konkol2019}'s attempt to reproduce of 41 geocomputational studies likewise found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures created using the original data and code deviated from the those published in some significant way (e.g., graphs with different curves).

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}
Reproducibility as a characteristic of a study that lends it credibility v. Reproducibility as a error correcting function of science.

@@

\subsection*{Assessing the Reproducibility of Geographic Research}
To date, only a small number of studies have attempted to reproduce geographic research.
The reproductions that are available within the discipline suggest that many studies cannot be fully reproduced \citep{Kedron2021ssrn, nust2018, ostermann2021}, or are simply missing the components needed to attempt a reproduction \citep{Kedron_VijayanRP, konkol2019, ostermann2021}.

For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be reproduced, or could only be reproduced with significant effort. 
A related effort to reproduce 31 papers published in the conference series of the Association of Geographic Information Laboratories in Europe \citep{Nust_AGILE_2020, Nust2021AGILE, Nust_AGILE_2022} similarly identified the inaccessibility of data, code, and information about the computational environment as key barriers to recreating results. 
\citet{konkol2019}'s attempt to reproduce of 41 geocomputational studies likewise found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures created using the original data and code deviated from the those published in some significant way (e.g., graphs with different curves).

@@

\subsection{Survey Demographics}

\subsection{Definition of Reproducibility}
Definition Questions and Q8 about beliefs about the interpretation for reproductions. Dig into those respondents that had variations in beliefs on Q8 sequence. Q17 about importance of reproduction. Close with Q13.

\subsection{Familiarity and Frequency of Practices}
Summary of Table showing Familiarity 1) all survey, 2) Methods, 3) Subfield Split
Summary of Table showing Implementation 1) all survey, 2) Methods, 3) Subfield Split

\subsection{Actual Reproductions}
Summary of Q10-Q12

\subsection{Barriers to Reproduction}
Q14
